Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-24 manuscript/manuscript.Rmd
added flow chart

header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{lineno}
  - \usepackage{setspace}
  - \usepackage{bookmark}
  - \usepackage{float}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage{subcaption}
  - \linenumbers
  - \doublespacing

@@

$$
  f(X_t) = r X_t\big(1 - X_t / K \big) =: L(X_t;\ r, K).
$$
The model this $f$ gives rise to is known as the Gordon-Schaefer model, after foundational work which first developed the concept of maximum sustainable yield, MSY, [@Gordon1954; @Schaefer1954], which remains a central concept in fisheries management.
In this model, the maximum growth rate occurs at population size of $N = K/2$.
This value is approached asymptotically, from any positive initial state $N_0 \in (0,K)$, under a constant mortality $F = r/2$ policy.
At equilibrium this produces an asymptotic harvest of $rK/4$ per time step---the maximum yield sustainable indefinitely.

@@

\textbf{Probably just merge on previous sections.}
We consider a stochastic contribution to the system's dynamics.
This way, eq. \eqref{eq:may} becomes
\begin{align}
  \label{eq:may stoch}
  \Delta X_t
  = L(X_t;\ r, K) - F(X_t, H; \beta,c) - h_t + \eta_t,
\end{align}
where $\{\eta_t\}_t$ are independent Gaussian variables with zero mean.
The variance $\sigma^2$ of $\eta_t$ is an additional parameter of the model.

Similarly, eq. \eqref{eq:3d model} becomes
\begin{align*}
  \label{eq:3d model stoch}
  \begin{split}
    \Delta X_t &= L(X_t;\ r_X, K_X) - F(X_t, Z_t;\ \beta, c) - c_{XY}X_tY_t - h_t + \eta_{X,t},\\
    \Delta Y_t &= L(Y_t;\ r_Y, K_Y) - D F(Y_t, Z_t;\ \beta, c) - c_{XY}X_tY_t + \eta_{Y,t},\\
    \Delta Z_t &= \left(f(X_t + DY_t\right) - d_Z)Z_t + \eta_{Z,t}.
\end{split}
\end{align*}

@@

Here we review classical strategies for sustainable fishery management and we provide a birds-eye view of the alternative approach we propose.
A summary of the contrast between the two strategies is given in Fig. \ref{tbd}.

@@

There are several strategies that have been used to manage fisheries: *escapement*, *maximum sustainable yield (MSY)*, *total allowable catch (TAC)*, among others.
We collectively refere to these as *classical*, and will compare their performance to RL-based management strategies.
As shown in Fig. \ref{fig:tbd}, classical strategies have the common aspect of reducing the complex dynamics of the fishery ecosystem to a single equation governing the harvested population (say, $F$). 
A common example is using a logistic growth equation,
$$
  F_{t+1} - F_t = r F_t( 1 - F_t / K) - h_t =: L(F_t) - h_t,
$$
where the interaction between $F$ and its environment is summarized to two parameters, the growth rate $r$, and the carrying capacity $K$.
In the equation above, $h_t$ is the *harvest* at timestep $t$.
The goal is to choose the harvest policy $h:F_t\mapsto h_t$ such that long-term profits are maximized.

>>>>

header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{lineno}
  - \usepackage{setspace}
  - \usepackage{bookmark}
  - \usepackage{float}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage{subcaption}
  - \usepackage{tikz-cd}
  - \linenumbers
  - \doublespacing

@@

\begin{align}
  \label{eq:logistic}
  f(X_t) = r X_t\big(1 - X_t / K \big) =: L(X_t;\ r, K).
\end{align}

The model this $f$ gives rise to is known as the Gordon-Schaefer model, after foundational work which first developed the concept of maximum sustainable yield, MSY, [@Gordon1954; @Schaefer1954], which remains a central concept in fisheries management.
In this model, the maximum growth rate occurs at population size of $N = K/2$.
This value is approached asymptotically, from any positive initial state $N_0 \in (0,K)$, under a constant mortality $F = r/2$ policy.
At equilibrium this produces an asymptotic harvest of $rK/4$ per time step---the maximum yield sustainable indefinitely.

@@

We have, up to now, presented eqs. \eqref{eq:may} and \eqref{eq:3d model} as *deterministic* dynamical models for the sake of clarity.
In practice, we will consider a stochastic contribution to these dynamics.
This way, instead of eq. \eqref{eq:may}, we consider the following stochastic single-species system
\begin{align}
  \label{eq:may stoch}
  \Delta X_t
  = L(X_t;\ r, K) - F(X_t, H; \beta,c) - h_t + \eta_t,
\end{align}
where $\{\eta_t\}_t$ are independent Gaussian variables with zero mean.
The variance $\sigma^2$ of $\eta_t$ is an additional parameter of the model.

Similarly, we use the following dynamical model in place of eq. \eqref{eq:3d model}
\begin{align*}
  \label{eq:3d model stoch}
  \begin{split}
    \Delta X_t &= L(X_t;\ r_X, K_X) - F(X_t, Z_t;\ \beta, c) - c_{XY}X_tY_t - h_t + \eta_{X,t},\\
    \Delta Y_t &= L(Y_t;\ r_Y, K_Y) - D F(Y_t, Z_t;\ \beta, c) - c_{XY}X_tY_t + \eta_{Y,t},\\
    \Delta Z_t &= \left(f(X_t + DY_t\right) - d_Z)Z_t + \eta_{Z,t}.
\end{split}
\end{align*}
Here, again, $\{\eta_{i,t}\}$ is a set of independent Gaussian variables centered at zero with variances, respectively, $\sigma_X^2$, $\sigma_Y^2$ and $\sigma_Z^2$.

@@

Here we review classical strategies for sustainable fishery management and we provide a birds-eye view of the alternative approach we propose.
A summary of the contrast between the two strategies is given in Fig. \ref{fig:decision approaches}.

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/DecisionApproaches.pdf}
  \caption{
  \label{fig:decision approaches}
  TBD.
  }
\end{figure}

@@

There are several strategies that have been used to manage fisheries: *escapement*, *maximum sustainable yield (MSY)*, *total allowable catch (TAC)*, among others.
We collectively refere to these as *classical*, and will compare their performance to RL-based management strategies.
Classical strategies derive an optimal harvest policy using a simple model for the system dynamics.
While often complex models of the ecosystem are used to estimate the fish population of interest (i.e. $X_t$), the quota is set only taking into account the estimate $X_t$.
The function determining this quota is derived from a simple dynamical model for the population (see text box 1).

\textbf{Text box 1 (TBD formatting)}
Let us consider a ubiquitous simple example: an MSY policy based on a logistic growth model for $X_t$ (see eqs. \eqref{eq:general model} and \eqref{eq:logistic}).

Classical strategies have the common aspect of reducing the complex dynamics of the fishery ecosystem to a single equation governing the harvested population (say, $F$). 
A common example is using a logistic growth equation,
$$
  F_{t+1} - F_t = r F_t( 1 - F_t / K) - h_t =: L(F_t) - h_t,
$$
where the interaction between $F$ and its environment is summarized to two parameters, the growth rate $r$, and the carrying capacity $K$.
In the equation above, $h_t$ is the *harvest* at timestep $t$.
The goal is to choose the harvest policy $h:F_t\mapsto h_t$ such that long-term profits are maximized.
